Notes on modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-06-17 docs/mvfits_paper/mvf.tex
updating doc with alos templates

% Generic greedy algo
\hspace{1cm}
{\scriptsize
\begin{algorithm}[H]
  %
  \caption{A positive (forward) greedy algorithm, \texttt{PGREEDY}}
  \label{alg:pgreedy}
  %
  \begin{algorithmic}[1]
    %
    \State {\bf Input:} $ \{ \mlam_{bulk} = \text{basis symbols}$, $\mathcal{A} = \text{action}$, $tol=\text{greedy tolerance}\}$
    \vskip 10pt
    \State Define empty list of kept symbols: $\mlam_{kept} = \{\}$
    \State Initialize estimator value and loop boolean: $\epsilon_{last} = \mathrm{inf}$, $done = \text{False}$
    %
    \While{not $done$}
      \State $\epsilon_{min} = \epsilon_{last}$
      %
      \For { $\mlam$ in $\mlam^{bulk}$ }
        \State $\mlam_{trial} = \mlam_{kept} \cup \mlam$ {\hskip0.525in} (add $\mlam$ to $\mlam_{kept}$)
        \State $\epsilon = \mathcal{A}(\mlam_{trial})$ {\hskip0.725in} (apply action)
        \If { $\epsilon < \epsilon_{min}$ }
          \State $\epsilon_{min} = \epsilon$  {\hskip0.725in} (store trial min)
          \State $\mlam_{min} = \mlam_{trial}$
        \EndIf
      \EndFor
      %
      \State $done = |\epsilon_{min}-\epsilon_{last}|<tol$ {\hskip0.4in} (determine if estimator has changed significantly)
      \If { not $done$ }
        \State $\epsilon_{last} = \epsilon_{min}$
        \State $\mlam_{kept} = \mlam_{kept} \cup \mlam_{min}$ {\hskip0.4in} (update kept symbols)
      \EndIf
      %
    \EndWhile
    \vskip 10pt
    \State {\bf Output:} Greedy Basis, $\{ \mlam_{kept} \}$
    %
  \end{algorithmic}
  %
\end{algorithm}
}

>>>>

% Forward greedy algo
\hspace{1cm}
{\scriptsize
\begin{algorithm}[H]
  %
  \caption{A positive (forward) greedy algorithm, \texttt{PGREEDY}. Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error. In this setting, $\mathcal{A}$ is assumed to have access to peropheral information, such as the training data.}
  \label{alg:pgreedy}
  %
  \begin{algorithmic}[1]
    %
    \State {\bf Input:} $ \{ \mlam_{bulk} = \text{basis symbols}$, $\mathcal{A} = \text{action}$, $tol=\text{greedy tolerance}\}$
    \vskip 10pt
    \State Define empty list of kept symbols: $\mlam_{kept} = \{\}$
    \State Initialize estimator value and loop boolean: $\epsilon_{last} = \mathrm{inf}$, $done = \text{False}$
    %
    \While{not $done$}
      \State $\epsilon_{min} = \epsilon_{last}$
      %
      \For { $\mlam$ in $\mlam^{bulk}$ }
        \State $\mlam_{trial} = \mlam_{kept} \cup \mlam$ {\hskip0.525in} (add $\mlam$ to $\mlam_{kept}$)
        \State $\epsilon = \mathcal{A}(\mlam_{trial})$ {\hskip0.70in} (action returns fit error)
        \If { $\epsilon < \epsilon_{min}$ }
          \State $\epsilon_{min} = \epsilon$  {\hskip0.825in} (store trial min)
          \State $\mlam_{min} = \mlam_{trial}$
        \EndIf
      \EndFor
      %
      \State $done = |\epsilon_{min}-\epsilon_{last}|<tol$ %{\hskip0.4in} (determine if estimator has changed significantly)
      \If { not $done$ }
        \State $\epsilon_{last} = \epsilon_{min}$
        \State $\mlam_{kept} = \mlam_{kept} \cup \mlam_{min}$ {\hskip0.4in} (update kept symbols)
      \EndIf
      %
    \EndWhile
    \vskip 10pt
    \State {\bf Output:} Greedy Basis, $\{ \mlam_{kept} \}$
    %
  \end{algorithmic}
  %
\end{algorithm}
}

% GMVP
\hspace{1cm}
{\scriptsize
\begin{algorithm}[H]
  %
  \caption{\gmvp{}, a degree tempered stepwise algorithm for multivariate polynomial modeling of scalar data.}
  \label{alg:pgreedy}
  %
  \begin{algorithmic}[1]
    %
    \State {\bf Input:} $ \{ \bf{x}, \bf{y} \}$
    \vskip 10pt
    \State Define action using matrix least squares
    \State Define bulk symbol space using cartesian inner-product
    \State Define list of allowed polynomial degrees
    \For { all degrees }
      \State Select all symbols with degree less than or equal to current
      \State Apply \texttt{PGREEDY} to get symbol subset and estimator val
      \If  { estimator has stalled }
        \State Break
      \EndIf
    \EndFor
    \State Apply negative greedy to get final model
    \vskip 10pt
    \State {\bf Output:} Final model
    %
  \end{algorithmic}
  %
\end{algorithm}
}

% GMVR
\hspace{1cm}
{\scriptsize
\begin{algorithm}[H]
  %
  \caption{\gmvr{}, a degree tempered stepwise algorithm for multivariate rational modeling of scalar data.}
  \label{alg:pgreedy}
  %
  \begin{algorithmic}[1]
    %
    \State {\bf Input:} $ \{ \bf{x}, \bf{y} \}$
    \vskip 10pt
    \State Define action using matrix least squares
    \State Define bulk symbol space using cartesian inner-product
    \State Define list of allowed polynomial degrees
    \For { all degrees }
      \State Select all numerator symbols with degree less than or equal to current
      \State Select all denominator symbols with degree less than or equal to current, enforcing no constant term
      \State Construct new symbol space by tagging each polynomial symbol with a boolean denoting whether it is in the numerator or denominator
      \State Apply \texttt{PGREEDY} to get symbol subset and estimator val
      \If  { estimator has stalled }
        \State Break
      \EndIf
    \EndFor
    \State Apply negative greedy to get final model
    \vskip 10pt
    \State {\bf Output:} Final model
    %
  \end{algorithmic}
  %
\end{algorithm}
}
